Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
adverbs
Unneccessary : It should be noted that.

Other simulation inputs are outlined in \Cref{table:params}. It should be noted
that the reactor simulation height of 151.75 cm was chosen to produce an
approximately critical reactor configuration corresponding to \gls{BOL}
\gls{MSRE} composition. It is about 10 cm shorter than the actual \gls{MSRE}
height of 162.56 cm.

@@

\Cref{fig:pre1} shows the concentration of the longest lived precursor in the
reactor. Not surprisingly, the channel concentrations are higher in fuel channels
with higher neutron fluxes and consequently a higher number of fission
events. Because of the small decay constant of the precursor, the maximum
concentration in any given channel occurs at the core outlet due to advection.

>>>>

Other simulation inputs are outlined in \Cref{table:params}.
The reactor simulation height of 151.75 cm was chosen to produce an
approximately critical reactor configuration corresponding to \gls{BOL}
\gls{MSRE} composition. It is about 10 cm shorter than the actual \gls{MSRE}
height of 162.56 cm.

@@

\Cref{fig:pre1} shows the concentration of the longest lived precursor in the
reactor. Not surprisingly, the channel concentrations are higher in fuel channels
with higher neutron fluxes and corresponding fission
events. Because of the small decay constant of the precursor, the maximum
concentration in any given channel occurs at the core outlet due to advection.
